---
title: "R Notebook"
output: html_notebook
---

weeks 6 day 5 homework



```{r}
library(tidyverse)
library(ggplot2)
library(janitor)
library(infer)
library(here)
sleep_data <-  msleep

sleep_data

nrow(sleep_data)
colnames(sleep_data)
unique(sleep_data$sleep_total) ## no NA values = good
sort(unique(sleep_data$name))
```


```{r}
t.test(sleep_data$sleep_total)
```

the jabberwakos sleep is 7 hours as denoted by mu
the confidernece intervul at 95% from the Ttest is 9.46 to 11.405
7 is outside this window and as such we can say that jabberwoks have a statistically lower ammount of sleep than the other animals
i also have no idea if this is the right way of doing it, these stats are messing with my head, uni PTSD is at critical levels
HAAAALLLLPPPP MEEEEEEEEE!!!!

```{r}
omni = filter(sleep_data, vore == "omni")
omni = omni$sleep_total
herb = filter(sleep_data, vore == "herbi")
herb = herb$sleep_total
t.test(omni, herb, alternative = "two.sided", var.equal = FALSE)


### i made that up, so heres what i think im supposed to be doing below
######################################################################

sleep_data_by_vore <-  sleep_data %>%
  filter(vore %in% c("omni", "herbi")) %>%
  group_by(vore)

null_distribution <- sleep_data_by_vore %>%
  specify(sleep_total ~ vore)%>%
  hypothesise(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("omni", "herbi"))


observed_stat <- sleep_data_by_vore%>%
  specify(sleep_total ~ vore) %>%
  calculate(stat = "diff in means", order = c("omni", "herbi"))

null_distribution %>%
  visualize()+
  shade_p_value(obs_stat = observed_stat, direction = "right")

```

the p vlaue is greater than 0.1 which suggests a general trend dut weak evidence that the means are the same
this lends credence to the idea that the sleep dureations are different but im bad at math so i have no idea

the second test shows the graph, i think its somehow usefull


```{r}

```


